Visualization

### 2020-10-12 analysis/visualization.Rmd

#Visualizing FD trends
```{r}
#load(here::here("data", "fd_table.rda"))
fd_table <- pins::pin_get("fd_table", board = "github")

@@

plot_metric <- function(metric_name, ylabel){
  data <- fd_table %>%
    filter(metric == metric_name) %>%
    mutate(plot_id = as.factor(plot_id), logvalue = log(value))

  mod <- lmer(logvalue ~ year + (1|plot_id), data = data)
  coefs <- summary(mod)$coefficients

@@

  trend_plot <- data %>%
    left_join(pred, by = "year") %>%
    #left_join(metadata %>% select(study_id, climate)) %>%
    ggplot(aes(x = year, y = logvalue)) +
    # geom_smooth(aes(color = climate, group = plot_id), method = "glm", se = FALSE) +
    # geom_point(aes(color = climate, group = plot_id)) +
    geom_point(aes(group = plot_id) ,color = "grey") +
    geom_smooth(aes(group = plot_id), color = "darkgrey", method = "glm", se = FALSE) +
    #geom_smooth(color = "black", method = "glm", se = FALSE) +
    geom_line(mapping = aes(y = pred)) +
    theme(legend.position = "none") +
    theme_classic() +
    ylab(ylabel)

@@

get model info
```{r}
get_metric_conint <- function(metric_name){
 data <- fd_table %>%
    filter(metric == metric_name) %>%
    mutate(plot_id = as.factor(plot_id), logvalue = log(value))

  mod <- lmer(logvalue ~ year + (1|plot_id), data = data)
  coefs <- summary(mod)$coefficients

>>>>

#Visualizing FD trends
```{r}
#load(here::here("data", "fd_table.rda"))
fd_table <- pins::pin_get("fd-table", board = "github")

@@

plot_metric <- function(metric_name, ylabel){
  data <- fd_table %>%
    filter(metric == metric_name) %>%
    mutate(plot_id = as.factor(plot_id), logSES = log(SES))

  mod <- lmer(logSES ~ year + (1|plot_id), data = data)
  coefs <- summary(mod)$coefficients

@@

  trend_plot <- data %>%
    left_join(pred, by = "year") %>%
    #left_join(metadata %>% select(study_id, climate)) %>%
    ggplot(aes(x = year, y = logSES)) +
    # geom_smooth(aes(color = climate, group = plot_id), method = "glm", se = FALSE) +
    # geom_point(aes(color = climate, group = plot_id)) +
    geom_point(aes(group = plot_id) ,color = "grey") +
    geom_smooth(aes(group = plot_id), color = "darkgrey", method = "glm", se = FALSE) +
    #geom_smooth(color = "black", method = "glm", se = FALSE) +
    geom_line(mapping = aes(y = pred)) +
    theme(legend.position = "none") +
    theme_classic() +
    ylab(ylabel)

@@

get model info
```{r}
get_metric_conint <- function(metric_name){
 data <- fd_table %>%
    filter(metric == metric_name) %>%
    mutate(plot_id = as.factor(plot_id), logSES = log(SES))

  mod <- lmer(logSES ~ year + (1|plot_id), data = data)
  coefs <- summary(mod)$coefficients
